How explicit is the Explicit Formula?

### 2016-08-02 paper/paper.tex
william tiny changes

\begin{align*}
{\bf (*)}\ \ \ \sum_{n} {\frac{1}{n}}\pi(X^{{\frac{1}{n}}}) \ \ \ &= \\
  {\rm Li}(X) \ \ \  +& \ \ \  \left\{ \int_X^{\infty}{\frac{1}{x^2-1}}\cdot {\frac{dx}{x\log(x)}} +\log(\xi(0))\right\}\ \ \ \     - \ \ \   \sum_\theta({\rm Li}(X^{{\frac{1}{2}}+i\theta})+ {\rm Li}(X^{{\frac{1}{2}}-i\theta})).
\end{align*}

Here,  the Riemann Hypothesis is assumed,
 the $\pm \theta$ are the imaginary parts of the nontrivial zeroes, and  $\xi(0)$ is---it seems---a scribe's error for  $\zeta(0)=1/2$.%
%Riemann obtains his formula by analyzing   $\log\zeta(s)$ which is $\sum_p \log(1+p^{-s)}$  for ${\rm Re}(s) > 1$  and dealing with poles and zeroes by means of the Cauchy integral theorem
  The three terms on the right correspond to, respectively:  the pole of $\zeta(s)$ at $s=1$, the trivial zeroes of $\zeta(s)$, and the nontrivial zeroes of $\zeta(s)$.

@@

@@

   The   values of  ${\mathcal D}_E(X)$ achieve a  limiting distribution $\mu_E$ (with respect to multiplicative Haar measure $dx/x$) with {\it mean} $M$ equal to $1- 2r_E$  and variation  $V$  equal to $$\lim_{T \to \infty} \sum_{|\gamma | \le T}{\frac{1}{{\frac{1}{4}} + \gamma^2}}.$$

@@

To have some vocabulary to deal with its statistics, consider

$$U_n(\theta) : = {\frac {\sin(n+1)\theta}{\sin\theta}}$$  so we have:

  $$\frac{a_E(p)}{\sqrt p} = U_1(\theta_{E,p}).$$  Note that the set $\{U_n\}$ for $n=0,1,2,\dots$ forms an orthonormal basis of the Hilbert space $L^2[0,\pi]$  with the
 inner product

@@

[[idea -- instead just define $\Phi(H,T)$ to be the min
of the finitely many possible linear combinations, and ask
about the behavior of $\Phi$.  Is there some clever algorithm
to get information about this?]]
\end{itemize}\end{itemize}
\end{document}
  \centerline{ $E = 11a$}
 \vskip10pt
 \includegraphics[width=0.9\textwidth]{plots/OSC11.pdf}

>>>>

\begin{align*}
{\bf (*)}\ \ \ \sum_{n} {\frac{1}{n}}\pi(X^{{\frac{1}{n}}}) \ \ \ &= \\
  {\rm Li}(X) \ \ \  +& \ \ \  \left\{ \int_X^{\infty}{\frac{1}{x^2-1}}\cdot {\frac{dx}{x\log(x)}} +\log(\xi(0))\right\}\ \ \ \     - \ \ \
  \sum_\theta\left({\rm Li}(X^{{\frac{1}{2}}+i\theta})+ {\rm Li}(X^{{\frac{1}{2}}-i\theta})\right).
\end{align*}

Here,  the Riemann Hypothesis is assumed,
 the $\pm \theta$ are the imaginary parts of the nontrivial zeroes, and  $\xi(0)$ is---it seems---a scribe's error for  $\zeta(0)=1/2$.
%Riemann obtains his formula by analyzing   $\log\zeta(s)$ which is $\sum_p \log(1+p^{-s)}$  for ${\rm Re}(s) > 1$  and dealing with poles and zeroes by means of the Cauchy integral theorem
The three terms on the right correspond to, respectively:  the pole of $\zeta(s)$ at $s=1$, the trivial zeroes of $\zeta(s)$, and the nontrivial zeroes of $\zeta(s)$.

[[William: we need to address the fact that the above
formula is somehow nonsense, right?     See worksheets/2016-06-08-150036-very-explicit-zeta-formula.sagews]]

@@

[[TODO: explain $T$, e.g., take limit as $T\to\infty$
or make error term depend on $T$.]]

@@

   The   values of  ${\mathcal D}_E(X)$ achieve a  limiting distribution $\mu_E$ (with respect to multiplicative Haar measure $dx/x$) with {\it mean} $M$ equal to $1- 2r_E$  and variance  $V$  equal to $$\lim_{T \to \infty} \sum_{|\gamma | \le T}{\frac{1}{{\frac{1}{4}} + \gamma^2}}.$$

@@

To have some vocabulary to deal with its statistics, consider
$$U_n(\theta) : = {\frac {\sin((n+1)\theta)}{\sin(\theta)}},$$
so we have:
  $$\frac{a_E(p)}{\sqrt p} = U_1(\theta_{E,p}).$$  Note that the set $\{U_n\}$ for $n=0,1,2,\dots$ forms an orthonormal basis of the Hilbert space $L^2[0,\pi]$  with the
 inner product

@@

[[idea -- instead just define $\Phi(H,T)$ to be the min
of the finitely many possible linear combinations, and ask
about the behavior of $\Phi$.  Is there some clever algorithm
to get information about this?]]
\end{itemize}\end{itemize}

  \centerline{ $E = 11a$}
 \vskip10pt
 \includegraphics[width=0.9\textwidth]{plots/OSC11.pdf}
